Automated verification of stand-alone solar photovoltaic systems

### 2018-11-15 Tex/LaTeX2e Style File/Trindade_IEEE_journal_r2.tex
reviewed section 4
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{flowchart_verification.png}
\centering
\caption{Flowchart of the proposed automated verification of PV systems.}
\label{fig:flowchartgeneral}
\end{figure}

@@

In a nutshell, ESBMC will process the C code with constraints ($C$) and properties ($P$) from the PV system that were inputted by the user, and the tool will verify automatically if the requirements are met. If the return is a fail, then the tool details the condition of violation, i.e., the state of each variable related to the system. That information can be used as a feedback to improve the PV system project. In the other hand, if the verification succeeds, as indicated in Fig. \ref{fig:esbmcarch}, the PV system will present its intended behavior at the field.

>>>>

\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{flowchart_verification.png}
\centering
\caption{Flowchart of the proposed automated verification of PV systems. \textcolor{red}{shall we identify each step with a number? e.g., step 1, step 2, etc?}}
\label{fig:flowchartgeneral}
\end{figure}

@@

In a nutshell, ESBMC will process the C code with constraints ($C$) and properties ($P$) from the PV system that were inputted by the user, and the tool will verify automatically if the requirements are met. If the return is a fail, then the tool details the condition of violation, i.e., the state of each variable related to the system. That information can be used as a feedback to improve the PV system project. However, if the verification succeeds, as indicated in Fig. \ref{fig:esbmcarch}, the PV system will present its intended behavior at the field.

\textcolor{red}{The algorithm should be part of the methodology!!!}

\textcolor{red}{The case study should be described in the experimental evaluation section.}
